Working with the Poisson distribution

### 2023-01-12 src/pages.Rmd
Cleaned up 2018 files

```{r}
write_list <- function(page_year) {
  # get file list
  list.files(path=glue("../text/{page_year}", pattern="*.md")) %>%
    str_subset("md$") -> f
  # open files and find information
  source_list <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{page_year}/{fn}"))
    # get source
    source_list <- append(
      source_list,
      check_source(file_text))
    #get dates
    date_list <- append(
      date_list,
      check_dates(file_text))
  }
  # strip extensions
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> f
  n <- length(f)
  # search for problem files
  bad_date <- str_detect(date_list, "Error")
  bad_source <- str_detect(source_list, "Error")
  # create RMarkdown text
  links <- glue(
    "+ {date_list} ",
    "[{f}]",
    "(http://new.pmean.com/{f}/)  ")
  # store in a sorted data frame
  o <- order(date_list, f)
  return(
    data.frame(
      f, 
      links,
      date_list,
      source_list,
      bad_date,
      bad_source)[o, ])
}
```

```{r}
for (four_digit_year in c("2022")) {
  two_digit_year <- str_sub(four_digit_year, 3, 4)
  yaml_text <- write_yaml(two_digit_year)
  l <- write_list(two_digit_year)
  n <- dim(l)[1]
  fn <- glue("../text/{two_digit_year}/{four_digit_year}.md")
  write_lines(
    yaml_text, 
    file=fn,
    append=FALSE)
  write_lines(
    glue("New website ({n} files)\n\n"),
    file=fn,
    append=TRUE)
  write_lines(
    l$links, 
    file=fn,
    append=TRUE)
  problem_files <- c(
    paste(l$f, l$date_list)[l$bad_date],
    paste(l$f, l$source_list)[l$bad_source])
  all_good <- "All files passed data and source quality checks"
  if (length(problem_files)==0) problem_files <- all_good
  write_lines(
    c("\n", problem_files),
    file=fn,
    append=TRUE)
}
```

>>>>

```{r}
write_list <- function(page_year) {
  # get file list
  list.files(path=glue("../text/{page_year}", pattern="*.md")) %>%
    str_subset("md$") -> f
  # open files and find information
  source_list <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{page_year}/{fn}"))
    # get source
    source_list <- append(
      source_list,
      check_source(file_text))
    #get dates
    date_list <- append(
      date_list,
      check_dates(file_text))
  }
  # strip extensions
  f %>%
    str_replace(fixed(".Rmd"), "") %>%
    str_replace(fixed(".md"), "") -> f
  n <- length(f)
  # search for problem files
  bad_date <- str_detect(date_list, "Error")
  bad_source <- str_detect(source_list, "Error")
  old_source <- (!str_detect(source_list, "new")) & (!bad_source)
  old_link <- glue("Link to earlier page [here]({source_list}).")
  old_link[!old_source] <- ""
  # create RMarkdown text
  links <- glue(
    "+ {date_list} ",
    "[{f}]",
    "(http://new.pmean.com/{f}/). {old_link}  ")
  # store in a sorted data frame
  o <- order(date_list, f)
  return(
    data.frame(
      f, 
      links,
      date_list,
      source_list,
      bad_date,
      bad_source)[o, ])
}
```

```{r}
for (four_digit_year in c("2018")) {
  two_digit_year <- str_sub(four_digit_year, 3, 4)
  yaml_text <- write_yaml(two_digit_year)
  l <- write_list(two_digit_year)
  n <- dim(l)[1]
  fn <- glue("../text/{two_digit_year}/{four_digit_year}.md")
  write_lines(
    yaml_text, 
    file=fn,
    append=FALSE)
  write_lines(
    glue("New website ({n} files)\n\n"),
    file=fn,
    append=TRUE)
  write_lines(
    l$links, 
    file=fn,
    append=TRUE)
  problem_files <- c(
    paste(l$f, l$date_list)[l$bad_date],
    paste(l$f, l$source_list)[l$bad_source])
  all_good <- "All files passed data and source quality checks"
  if (length(problem_files)==0) problem_files <- all_good
  write_lines(
    c("\n", problem_files),
    file=fn,
    append=TRUE)
}
```

### 2023-01-12 text/21/poisson-inferences.Rmd
Cleaned up 2018 files

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: "New"
date: "2020-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---

>>>>

---
title: "Working with the Poisson distribution"
author: "Steve Simon"
source: new
date: "2021-08-30"
categories:
- Blog post
tags:
- Probability distributions
output: html_document
---
